\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{soul}
\usepackage{fullpage}
\usepackage{float}
\restylefloat{table}
\usepackage{tabto}
\usepackage{tikz}
\usetikzlibrary{positioning}
\newdimen\nodeDist
\nodeDist=35mm


\begin{document}

\begin{titlepage}
\begin{center}

% Upper part of the page. The '~' is needed because \\
% only works if a paragraph has started.


\textsc{\LARGE Delft University of Technology}\\[1.5cm]

\textsc{\Large IN4010 Practical Assignment 2}\\[0.5cm]

% Title
%\HRule \\[0.4cm]
{ \huge \bfseries Automated Negotiation \\[0.4cm] }

%\HRule \\[1.5cm]

% Author and supervisor
\noindent
\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Group 11:}\\
Hidde \textsc{Coehoorn}\\
Ralf \textsc{Nieuwenhuizen}\\
Jan-Willem \textsc{van Velzen}
\end{flushleft}
\end{minipage}%
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
Reyhan \textsc{Aydogan}
\end{flushright}
\end{minipage}

\vfill

% Bottom of the page
{\large \today}

\end{center}
\end{titlepage}

\newpage


\section{Introduction to assignment}

As part of the TU Delft course IN4010 Artificial Intelligence Techniques completion of a practical assignment on automated negotiation is required. This is the assignment report of group 11, of which the group members are Hidde Coehoorn, Ralf Nieuwenhuizen and Jan-Willem van Velzen.\\

The subject of the assignment is multilateral negotiation taking place in a multi-issue negotiation domain with discrete issues. The challenge is to design and implement a negotiating agent in GENIUS which can guide the negotiation process and help the parties involved with reaching a satisfying agreement. Various scenarios are created to test the agent, ranging in the degree of conflict between parties.\\

\input{domain}

\newpage

\input{agentdescription}

\input{tests}

\section{Conclusions}

We quite enjoyed discussing about the different actions our agent might take in different situations. As this was very close to real life, we could just think ``what would I do?'', and discuss about that. It all seemed very intuitive to us. It was also fun to invent and implement our own smart analyzing tools, like the OpponentUtilityModel. This way it really feels like we are making a smart person to analyze the opponent and do the negotiation for us.
\\\\
In order to be able to support human negotiations in the real world, our agent would need to understand some sort of input, and provide even more extensive output, to let the human know how he is reasoning. Apart from that, we think this agent is already quite versatile, as it can deal with various situations and always seems to find its way. The testing part may prove otherwise though, we are curious about that.
\\\\
To really take over the human negotiation, it would be nice to have some form of computer vision as well, to be able to recognize facial expressions in the opponents, and use that to determine their mood and their feelings regarding an offer. Apart from this, it should probably also be able to handle multiple offers at the same time, as human negotiation is unfortunately less structured than agent negotiation.

\newpage

\section*{Report requirements and checklist}

10 A4 pages may be enough, 15 A4 pages maximum\\
The report should include:\\
\begin{itemize}
\item \st{the group number}
\item an introduction to the assignment
\item a high-level description of the agent and its structure, including the main Java methods (mention
these explicitly!) used in the negotiating agent that have been implemented in the source code
\item an explanation of the negotiation strategy, decision function for accepting offers, any important
preparatory steps, and heuristics that the agent uses to decide what to do next, including the factors
that have been selected and their combination into these functions
\item a section documenting the tests you performed to improve the negotiation strength of your agent.
You must include scores of various tests over multiple sessions that you performed while testing
your agent. Describe how you set up the testing situation and how you used the results to modify
your agent
\item a conclusion in which you summarize your experience as a team with regards to building the
negotiating agent and discuss what extensions are required to use your agent in real-life negotiations
to support (or even take over) negotiations performed by humans.
\end{itemize}

\textbf{The final analysis report should involve an elaborate analysis of your agent's performance from different perspectives (e.g. individual utility gained, social welfare - the sum of utilities of all agents, optimality of the outcome, fairness etc.). NU NOG NIET NODIG}

\end{document}
